Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-05 tex/conclusion.tex
not 100% satisfied yet

In this thesis we explored how visual analytics can be used in order to leverage the full potential of black-box machine learning.
To this extend we used a variety of techniques to explain the behavior of machine learning models, both globally and locally, and developed a workflow to utilize those explanations to diagnose models.
We also studied the effect of aggregating local explanations in order to detect biases in the input data to models.
\todo{expand}

>>>>

In this thesis we explored how visual analytics can be used in order to leverage the full potential of black-box machine learning.
To this extend we used a variety of techniques to explain the behavior of machine learning models, both globally and locally, and developed a workflow to utilize those explanations to diagnose models.
We also studied the effect of aggregating local explanations in order to detect biases in the input data of machine learning models.
However, each finding shown in this thesis posed further questions, providing research opportunities to be investigated.

This thesis exhibited problems in the area of machine learning that can only be fully solved with human expertise.
In this context, visual analytics proved to be a powerful tool in assisting humans in performing this task.
Going forward, domain expertise remains an important role of humans in machine learning.
